\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Simplify the wording around DIaaS

Data Integrity as a Service (DIaaS) is a DLT-based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

>>>>

Data Integrity as a Service (DIaaS)\cite{DIaas} is a DLT-based framework for data integrity whichs deploys a Cloud Server Service (CSS) for both data providers and consumers to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Its contract can also realize the purchase agreement including authorization and penalization. However if the CSS is malicious or has crashed, losses to both providers and consumers will happen. Also, performance analysis shows that IoT devices are inefficient to interact with Ethereum due to the time-consuming Proof-of-Work(PoW) operations.
